WHAM MSE Pages

### 2025-04-16 docs/index.Rmd
trying long lived MSE setup, currently breaking
adds output of base case and data poor scenarios

<a href="https://noaa-edab.github.io/WHAMmse_longlived/WorkflowDecisions.html" target="_blank"> Documenting long lived MSE workflow - April 2025 </a>

<a href="https://noaa-edab.github.io/WHAMmse_longlived/Results.html" target="_blank"> Initial results - April 2025 </a>

>>>>

<a href="https://noaa-edab.github.io/WHAMmse_longlived/MSEsetup.html" target="_blank"> Documenting long lived MSE workflow - April 2025 </a>

<a href="https://noaa-edab.github.io/WHAMmse_longlived/Scenarios.html" target="_blank"> Single run of base and data degradation scenarios - April 2025 </a>
